Outbreak Threshold Detection

### 2023-08-16 notebooks/Julia/simulation-detection.qmd
Rename epsilon vars for clarity
Rewrite numbers to use _ to delimit every thousand
Rename init_states var for clarity

u₀ = [999.0, 10.0, 0.0, 0.0]

mu = 1
beta = 1000
sigma = 365/8
gamma = 365/5
ε = 100
p = (beta, sigma, gamma, mu, ε)
```

@@

prob = DiscreteProblem(u₀, tspan, p)
jump_prob = JumpProblem(prob, Coevolve(), gillespie_jumps...; dep_graph)
sol = solve(jump_prob, SSAStepper())
sol_array = zeros(6, length(sol))
sol_array[1:4, :] = Array(sol)[1:4, :]
sol_array[5, :] = sum(sol_array[1:4, :], dims = 1)
sol_array[6, :] = sol.t
```

@@

```{julia}
function run_sir_sim(; u₀, tspan, p)
    prob = DiscreteProblem(u₀, tspan, p)
    jump_prob = JumpProblem(
        prob, Coevolve(), gillespie_jumps..., save_positions = (false, false);
        dep_graph
        )
    jump_sol = solve(jump_prob, SSAStepper(), saveat = δt)
    return jump_sol;
end
```

@@

@showprogress for i in 1:nsims
    out_jump = run_sir_sim(u₀ = u₀, tspan = tspan, p = p)
    create_sim_array!(out_jump = out_jump)

>>>>

init_states = [999.0, 10.0, 0.0, 0.0]

mu = 1
beta = 1_000
sigma = 365/8
gamma = 365/5
epsilon = 100
p = (beta, sigma, gamma, mu, epsilon)
```

@@

prob = DiscreteProblem(init_states, tspan, p)
jump_prob = JumpProblem(prob, Coevolve(), gillespie_jumps...; dep_graph)
sol = solve(jump_prob, SSAStepper())
sol_array = zeros(6, length(sol))
sol_array[1:4, :] = Array(sol)[1:4, :]
sol_array[5, :] = sum(sol_array[1:4, :], dims = 1)
sol_array[6, :] = sol.t
```

@@

```{julia}
function run_sir_sim(; init_states, tspan, p)
    prob = DiscreteProblem(init_states, tspan, p)
    jump_prob = JumpProblem(
        prob, Coevolve(), gillespie_jumps..., save_positions = (false, false);
        dep_graph
        )
    jump_sol = solve(jump_prob, SSAStepper(), saveat = δt)
    return jump_sol;
end
```

@@

@showprogress for i in 1:nsims
    out_jump = run_sir_sim(init_states = init_states, tspan = tspan, p = p)
    create_sim_array!(out_jump = out_jump)
